### 2021-06-15 abstract-jss.tex
abstract improvements

\begin{abstract}
  The use of sandboxes is an effective technique for malware analysis. However, although the use of dynamic analysis for mining Android sandboxes has been investigated before, little is known about the potential benefits of combining static and dynamic analysis for mining Android sandboxes.
Accordingly, in this paper we present the results of two studies that investigate whether or not static analysis might complement and increase the performance of dynamic analysis tools for mining Android sandboxes. %\emph{Method.} 
In the first study we conduct a non-exact replication of the Bao et al. work, a previous study that compares the performance of test case generation tools for mining Android sandboxes. Differently from the original work, here we isolate the effect of the static analysis tool (DroidFax) they used to instrument the Android apps in their experiments. This decision was motivated by the fact that DroidFax could have influenced the efficacy of the dynamic analyses positively---through the execution of specific static analysis algorithms. In our second study, we carried out a new experiment to investigate the efficacy of tainted analysis algorithms for mining Android sandboxes. To this end, we executed the FlowDroid tool to mine the source-sink flows from the benign/malign pairs of Android apps used in the Bao et al. study. %\emph{Results.}
Our study brings several findings. For instance, the first study reveals that DroidFax alone (static analysis) can detect 43.75\% of the malwares in the dataset of the Bao et al. work, leading to an overestimation of the performance of the dynamic analysis tools. The results of the second study show that (static) tainted analysis is also practical for mining Android sandboxes, with a performance similar to that reached by dynamic analysis tools.
\end{abstract}

>>>>

\begin{abstract}
%  \emph{Context.}
The popularization of the Android platform and the growing number of Android apps that manage sensitive data turned the Android ecosystem into an attractive target for malicious software. For this reason, researchers and practitioners have investigated new approaches to address Android's security issues, including techniques that leverage dynamic analysis to \textit{mine Android sandboxes}. The mining sandbox approach consists in running fuzzing test tools into a benign version of the app. This exploratory phase records all calls to sensitive APIs. Later, we can use this information to (a) prevent calls to other sensitive APIs (those not recorded in the exploratory phase) or (b) run the fuzzing tools again in a different version of the app. During this second execution of the fuzzing tools, a warning of possible malicious behavior is raised whenever the new version of the app calls a sensitive API not recorded in the exploratory phase. 
%  \emph{Problem.}

The use of a mining sandbox approach is an effective technique for Android malware analysis, as previous research works revealed. Particularly, existing reports present an accuracy of almost 70\% in the identification of malicious behavior using dynamic analysis tools to mine android sandboxes. However, although the use of dynamic analysis for mining Android sandboxes has been investigated before, little is known about the potential benefits of combining static with a mining sandbox approach for identifying malicious behavior.
Accordingly, in this paper we present the results of two studies that investigate the impact of using static analysis to complement the performance of existing dynamic analysis tools tailored for mining Android sandboxes, in the task of identifying malicious behavior.
%\emph{Method.}

In the first study we conduct a non-exact replication of a previous study (hereafter \blls) that compares the performance of test case generation tools for mining Android sandboxes. Differently from the original work, here we isolate the effect of an independent  static analysis component (DroidFax) they used to instrument the Android apps in their experiments. This decision was motivated by the fact that DroidFax could have influenced the efficacy of the dynamic analyses positively---through the execution of specific static analysis algorithms. In our second study, we carried out a new experiment to investigate the efficacy of taint analysis algorithms to complement the mining Android sandbox approach previously used to identify malicious behavior. To this end, we executed the FlowDroid tool to mine the source-sink flows from benign/malign pairs of Android apps used in a previous research work. %\emph{Results.}

Our study brings several findings. For instance, the first study reveals that DroidFax alone (static analysis) can detect 43.75\% of the malwares in the \blls dataset, leading to an overestimation of the performance of the dynamic analysis tools. The results of the second study show that (static) taint analysis is also practical to complement mining Android sandboxes approach, with a performance similar to that reached by dynamic analysis tools.
\end{abstract}

### 2021-06-15 abstract.tex
abstract improvements

\begin{abstract}
%  \emph{Context.}
The popularization of the Android platform and the growing number of Android apps that manage sensitive data turned the Android ecosystem into an attractive target for malicious software. For this reason, researchers and practitioners have investigated new approaches to address Android's security issues, including techniques that leverage dynamic analysis to \textit{mine Android sandboxes}. 
%  \emph{Problem.}
The use of sandboxes is an effective technique for malware analysis. However, although the use of dynamic analysis for mining Android sandboxes has been investigated before, little is known about the potential benefits of combining static and dynamic analysis for mining Android sandboxes.
Accordingly, in this paper we present the results of two studies that investigate whether or not static analysis might complement and increase the performance of dynamic analysis tools for mining Android sandboxes. %\emph{Method.} 
In the first study we conduct a non-exact replication of the Bao et al. work, a previous study that compares the performance of test case generation tools for mining Android sandboxes. Differently from the original work, here we isolate the effect of the static analysis tool (DroidFax) they used to instrument the Android apps in their experiments. This decision was motivated by the fact that DroidFax could have influenced the efficacy of the dynamic analyses positively---through the execution of specific static analysis algorithms. In our second study, we carried out a new experiment to investigate the efficacy of taint analysis algorithms to complement mining Android sandboxes. To this end, we executed the FlowDroid tool to mine the source-sink flows from the benign/malign pairs of Android apps used in the Bao et al. study. %\emph{Results.}
Our study brings several findings. For instance, the first study reveals that DroidFax alone (static analysis) can detect 43.75\% of the malwares in the dataset of the Bao et al. work, leading to an overestimation of the performance of the dynamic analysis tools. The results of the second study show that (static) taint analysis is also practical to complement mining Android sandboxes approach, with a performance similar to that reached by dynamic analysis tools.
\end{abstract}

>>>>

\begin{abstract}
%  \emph{Context.}
The popularization of the Android platform and the growing number of Android apps that manage sensitive data turned the Android ecosystem into an attractive target for malicious software. For this reason, researchers and practitioners have investigated new approaches to address Android's security issues, including techniques that leverage dynamic analysis to \textit{mine Android sandboxes}. The mining sandbox approach consists in running fuzzing test tools into a benign version of the app. This exploratory phase records all calls to senstive appis. Later, we can use this information to (a) prevent calls to other sensitive APIs (those not recorded in the exploratory phase) or (b) run the fuzzing tools again in a different version of the app. During this second execution of the fuzzing tools, a warning of possible malicious behavior is raised whenever the new version of the app calls a sensitive API not recorded in the exploratory phase. 
%  \emph{Problem.}
The use of a mining sandbox approach is an effective technique for Android malware analysis, as previous research works revealed. Particularly, existing reports present an accuracy of almost 70\% in the identification of malicious behavior using dynamic analysis tools to mine android sandboxes. However, although the use of dynamic analysis for mining Android sandboxes has been investigated before, little is known about the potential benefits of combining static and dynamic analysis for identifying malicious behavior.
Accordingly, in this paper we present the results of two studies that investigate the impact of using static analysis to complement the performance of existing dynamic analysis tools in the task of identifying malicious behavior.
%\emph{Method.} 
In the first study we conduct a non-exact replication a previous study that compares the performance of test case generation tools for mining Android sandboxes. Differently from the original work, here we isolate the effect of an independent  static analysis component (DroidFax) they used to instrument the Android apps in their experiments. This decision was motivated by the fact that DroidFax could have influenced the efficacy of the dynamic analyses positively---through the execution of specific static analysis algorithms. In our second study, we carried out a new experiment to investigate the efficacy of taint analysis algorithms to complement the mining Android sandbox approach previously used to identify malicious behavior. To this end, we executed the FlowDroid tool to mine the source-sink flows from benign/malign pairs of Android apps used in a previous research work. %\emph{Results.}
Our study brings several findings. For instance, the first study reveals that DroidFax alone (static analysis) can detect 43.75\% of the malwares in the dataset of the work we replicated in this study, leading to an overestimation of the performance of the dynamic analysis tools. The results of the second study show that (static) taint analysis is also practical to complement mining Android sandboxes approach, with a performance similar to that reached by dynamic analysis tools.
\end{abstract}
